Title

### 2024-05-07 paper/main.tex
Updates

\section{Empirical Analysis}
We performed empirical analysis to compare how well does creating a graph manually based on effect sizes and p-value compare to algorithmic approaches.
\subsection{Simulating an expert}
To simulate an expert building a model manually, we wrote a simple greedy simulation as shown in the Figure. The expert always starts with a graph with
no edges and chooses the pair of variables with the highest correlation between them. The expert based on some accuracy measure decides the direction
of the edge between these variables such that the new added edge does not create a cycle in the DAG:

\todo{Summarize this section and equaiton in an algorithm}
\begin{equation}
	\begin{split}
		x &= \textnormal{rand}([0, 1]) \\
		O(\alpha) &= \begin{cases} 
			M \rightarrow Y, & \textnormal{if  } x <= \alpha \\
			\textnormal{rand}(M \rightarrow Y, M \leftarrow Y, None) & \textnormal{otherwise} \\
			     \end{cases} \\
	\end{split}
\end{equation}

>>>>

\section{Empirical Analysis}
To compare how well does creating a graph manually based on effect sizes and
p-value compare to algorithmic approaches, we performed some emperical
analysis.

\subsection{Simulating an expert}
To simulate an expert building a model manually, we wrote a simple greedy simulation as shown in the Figure. The expert always starts with a graph with
no edges and chooses the pair of variables with the highest correlation between them. The expert based on some accuracy measure decides the direction
of the edge between these variables such that the new added edge does not create a cycle in the DAG.

\todo[inline]{Summarize this section and equaiton in an algorithm}
\todo[inline]{Show a consistency proof for this expert simulation}

\begin{equation}
	\begin{split}
		x &= \textnormal{rand}([0, 1]) \\
		O(\alpha) &= \begin{cases} 
			M \rightarrow Y, & \textnormal{if  } x <= \alpha \\
			\textnormal{rand}(M \rightarrow Y, M \leftarrow Y, None) & \textnormal{otherwise} \\
				\end{cases} \\
	\end{split}
\end{equation}
